brados: declarative, programmable object storage

### 2016-05-25 paper.tex

Ceph is designed to run on a wide variety of commodity hardware as well as new
NVMe devices, all of which their own set of characteristics and tunables (e.g.,
the IO operation scheduler type). In our experiments, we tested SSD, HDDs, NVMe
devices and discovered a wide range of behaviors and performance profiles.
Figure~\ref{fig:jewel-hdd-128b}, which shows the write performance of 128 by
log entries using Jewel and a single HDD, shows an especially tricky situation
for a developer.

In that figure, the performance is 10\(\times\) slower than its SSD counterpart
but performance of the N:1 bystestream implementation is almost identical to
the N:1 KV implementation (within 1\% mean throughput). Regardless of the true
bottleneck, it is clear that choosing the N:1 KV implementation is the better
choice because of the simple implementation and the minimal performance
degradation.

>>>>

Ceph is designed to run on a wide variety of commodity hardware as well as new
NVMe devices. All these devices have their own set of characteristics and
tunables (e.g., the IO operation scheduler type). In our experiments, we tested
SSD, HDDs, NVMe devices and discovered a wide range of behaviors and
performance profiles. As an example, Figure~\ref{fig:jewel-hdd-128b} shows the
write performance of 128 byte log entries using Jewel and a single HDD.
Performance is 10\(\times\) slower than its SSD counterpart in
Figure~\ref{ig:jewel_v_firefly_v_es} (top row, third column) but the behavior
and relative performance make this hardware configuration especially tricky.

The behavior of the 1:1 implementations shows throughput drops lasting for
minutes at a time -- this limits our focus to the N:1 implementations.

 The performance of the N:1 bystestream implementation is almost identical to
the N:1 KV implementation (within 1\% mean throughput). Regardless of the true
bottleneck, it is clear that choosing the N:1 KV implementation is the better
choice because of the simple implementation and the minimal performance
degradation.
